S4_countries

### 2021-12-23 S3_countries.Rmd
Update S3_countries.Rmd

#download data
# get the data directly from redcap:
# report #155 is Q1:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='155',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)
response <- httr::POST(url, body = formData, encode = "form")
Q1_table_countries <- httr::content(response)

>>>>

#download data
# get the data directly from redcap:
# report #155 is Q1:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "################################"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='155',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)
response <- httr::POST(url, body = formData, encode = "form")
Q1_table_countries <- httr::content(response)
